% Minimal ACCV/LNCS-oriented scaffold.
% If an official llncs.cls is available, this source can be migrated to
% \documentclass[runningheads]{llncs}. The current repository keeps a minimal
% dependency-free build path through scripts/build_paper.sh.
\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{url}
\title{Streaming Zero-Shot Industrial Anomaly Detection with CLIP}
\author{Anonymous ACCV Submission}
\date{}
\begin{document}
\maketitle
\begin{abstract}
TODO: Replace this placeholder abstract after real P0 results exist. This paper targets a CLIP-based zero-shot industrial anomaly detection evaluation protocol under streaming conditions. The current build intentionally avoids measured-result claims until \texttt{results/latest/manifest.json} is marked \texttt{final}.
\end{abstract}

\section{Introduction}
Industrial anomaly detection is often evaluated on static test sets, but practical inspection systems receive images over time. This scaffold focuses on the paper pipeline for a streaming CLIP-based zero-shot anomaly detection study.

TODO: Add evidence-backed motivation and citations.

\section{Evaluation Protocol}
The minimal P0 protocol covers MVTec AD and VisA, i.i.d. and bursty streams, prevalence 0.05, contamination levels 0, 0.01, and 0.05, and the baselines RareCLIP, PatchCore, WinCLIP, and AnomalyCLIP.

\section{Results}
TODO: Results are intentionally placeholders. Do not report measured AUROC, AUPR, ECE, latency, or CRD-lite until \texttt{results/latest/manifest.json} has \texttt{status: final} and \texttt{paper\_allowed: true}.

The paper may only consume result files from \texttt{results/latest/}.

\input{../results/latest/tables/baseline_summary.tex}

\section{Limitations}
TODO: Replace this section after real P0 runs. Expected interpretations from the protocol are not findings until validated by generated outputs.

\section*{References}
TODO: Add numeric citations in ACCV/LNCS style.

\end{document}
